---
title: "Alcohol vs Seat choice"
author: "Jasmine Walters"
date: "Spring 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  The median number of drinks of the back row is higher than the median of both front and back row. We can see that by looking at the boxes.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
  
There are "bites" on the boxes that are on the plot above. They represent the standard deviation, which is the amount of deviations among the data.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The size of the box goes from 0 to 12 and the others go from 0 to 4.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

## Conclusions

We reject the null hypothesis because the number is significantly low. The data we got was 0.000116.

```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```

Now that we have the box properly label, we can see that the 0 is only in the confidence between the front and the middle. Which tells us that the back is different than the both of them. This also shows that there is no statistically different between both the front and the middle. This is the case that both of them are the same and one is different from the others.